R, Python, and Ruby clients for GBIF species occurrence data

### 2020-02-27 use-cases/city-diversity.Rmd
tweaks to mee paper

```{r box}
url <- 'https://raw.githubusercontent.com/amyxzhang/
boundingbox-cities/master/boundbox.txt'
rawdat <- content(GET(sub("\n", "", url)), as = "text")
dat <- read.table(
  text = rawdat, header = FALSE,
  sep = "\t", col.names = c("city","minlat","maxlon","maxlat","minlon"),
  stringsAsFactors = FALSE)
dat <- data.frame(
  city = dat$city, minlon = dat$minlon,
  minlat = dat$minlat, maxlon = dat$maxlon,
  maxlat = dat$maxlat,
  stringsAsFactors = FALSE
)
```

>>>>

```{r box, cache=TRUE}
url <- 'https://raw.githubusercontent.com/amyxzhang/
boundingbox-cities/master/boundbox.txt'
rawdat <- content(GET(sub("\n", "", url)), as = "text")
dat <- read.table(
  text = rawdat, header = FALSE,
  sep = "\t", col.names = c("city","minlat","maxlon","maxlat","minlon"),
  stringsAsFactors = FALSE)
dat <- data.frame(
  city = dat$city, minlon = dat$minlon,
  minlat = dat$minlat, maxlon = dat$maxlon,
  maxlat = dat$maxlat,
  stringsAsFactors = FALSE
)
```

### 2020-02-27 use-cases/niche-modelling.Rmd
tweaks to use cases
tweaks to mee paper

```{r include=FALSE}
opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  comment = '#>',
  collapse = TRUE,
  cache.path = "cache/"
)
```

In this example, we plot actual occurrence data for _Bradypus_ species against a single predictor variable, BIO1 (annual mean temperature). This is only ont step in a species distribution modelling nworkflow.

@@

```{r}
library("rgbif")
library("dismo")
library("maptools")
library("dplyr")
```

>>>>

```{r include=FALSE}
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  comment = '#>',
  collapse = TRUE,
  cache.path = "cache/"
)
```

In this example, we plot actual occurrence data for _Bradypus_ species against a single predictor variable, BIO1 (annual mean temperature). This is only one step in a species distribution modelling workflow.

@@

```{r}
library("sp")
library("rgbif")
library("dismo")
library("maptools")
library("dplyr")
```
